Verifying Demonstrations

### 2018-05-25 paper/RelatedWork.tex

\seb{maybe we should also give information about the privacy level reached by 
  this different method}
From a privacy perspective, all techniques based on photo or video material are 
as privacy preserving as the protesters make themselves.
There is a risk that participants are recognizable from the material if they do 
not wear masks.

>>>>

From a privacy perspective, all techniques based on photo or video material are 
as privacy preserving as the protesters make themselves.
There is a risk that participants are recognizable from the material if they do 
not wear masks.
